This PDF is a Git Repository\\Containing its Own \LaTeX\ Source

### 2017-05-02 article.tex
Removed an unnecessary .
Added some whitespace above the arrows

\draw[<-] (b1) -- (type.south -| b1) node[anchor=north,align=center,font=\footnotesize] {if the MSB is one,\\then this is not\\the last byte};

@@

\draw[<-] (b9) -- (length.south -| b9) node[anchor=north,align=center,font=\footnotesize] {MSB is one,\\so this is \emph{not} the last byte};

@@

\draw[<-] (b17) -- (next.south -| b17) node[anchor=north,align=center,font=\footnotesize] {MSB is zero,\\so this is the last byte};

@@

Using our patched version of git, every object stored in the bundle
will be uncompressed!
\begin{center}
\begingroup
\setbox9=\hbox{\footnotesize\verb|$ git bundle create article_bundle.pdf --all|}
\begin{minipage}{\wd9}
\footnotesize\begin{verbatim}
$ export PATH=/path/to/patched/git:$PATH
$ git init .
$ git add article.pdf
$ git commit article.pdf -m "added"
$ git bundle create polyglot.pdf --all
\end{verbatim}
\end{minipage}
\endgroup
\end{center}

>>>>

\draw[<-] ([yshift=-2pt]b1.south) -- (type.south -| b1) node[anchor=north,align=center,font=\footnotesize] {if the MSB is one,\\then this is not\\the last byte};

@@

\draw[<-] ([yshift=-2pt]b9.south) -- (length.south -| b9) node[anchor=north,align=center,font=\footnotesize] {MSB is one,\\so this is \emph{not} the last byte};

@@

\draw[<-] ([yshift=-2pt]b17.south) -- (next.south -| b17) node[anchor=north,align=center,font=\footnotesize] {MSB is zero,\\so this \emph{is} the last byte};

@@

Using our patched version of git, every object stored in the bundle
will be uncompressed!
\begin{center}
\begingroup
\setbox9=\hbox{\footnotesize\verb|$ git bundle create article_bundle.pdf --all|}
\begin{minipage}{\wd9}
\footnotesize\begin{verbatim}
$ export PATH=/path/to/patched/git:$PATH
$ git init
$ git add article.pdf
$ git commit article.pdf -m "added"
$ git bundle create polyglot.pdf --all
\end{verbatim}
\end{minipage}
\endgroup
\end{center}
Any vanilla, un-patched version of git will be able to clone a repo
from the bundle. It will also be a valid PDF, since virtually all
PDF readers ignore garbage bytes before and after the PDF.

\section{Generalizing the PoC}

There are, of course, some
